Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2019-03-19 submission/manuscript.Rmd
First pass at Conclusion

**Conclusion.**

* Unlikely that SCFAs are the primary mechanism that limits tumorigenesis
* Limitations
	- Observing the community once the tumor is developed
	- Not looking at mucosal communities
* Need to identify other possible mechanisms that drive and prevent tumorigenesis
* Supports evidence that fiber consumption has a null effect on tumorigenesis

>>>>

**Conclusion.** Our data indicate that fecal SCFA concentrations are not associated with the presence of adenomas or carcinomas and that they provide weak predictive power to improve the ability to diagnose someone with one of these lesions. Furthermore, knowledge of the taxonomic and genetic structure of gut microbiota was not predictive of individual or pooled SCFA concentrations. These results complement existing literature that suggest that fiber consumption and the production of SCFAs are unable to prevent the risk of developing colonic tumors. It is important to note that our analysis concerned fecal SCFA concentrations and microbiome characterization and that observations along the mucosa near the site of lesions may provide a stronger association. Regardless, given the growing literature in this area, it is unlikely that SCFAs are the primary mechanism that limits tumorigenesis. This may be a cautionary result to temper enthusiasm for SCFAs as a biomarker of gut health more generally. Going forward it is critical to develop additional hypotheses for how the microbiome and host interact to drive tumorigenesis to better understand the disease process and identify biomarkers that will allow early detection of tumors.
